---
title: "Dashboard"
format:
  dashboard:
    expandable: false
---

```{r}
#| message: false
#| warning: false
#| include: false

# install.packages("D:/MDi/Documents/R/package20260206", repos = NULL, type = "source")
# install.packages("tidyverse")
# install.packages("forcats")
# install.packages("bslib")
# install.packages("bsicons")

library(package20260206)
library(tidyverse)
library(plotly)
library(forcats)
library(bslib)
library(bsicons)
library(htmltools)
```

# Production

```{r}
#| include: false
Production <- list()
#example: Production$Oil$Total
```

## _ {.tabset}

### Crude Oil {.tabset}

#### Total {.tabset-leaf}

```{r}
#| include: false
Oil_Total <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Total") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_Total %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_Total %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_Total %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_Total %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_Total %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_Total %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### In Situ Bitumen {.tabset-leaf}

```{r}
# EF2023$crude_oil_production %>%
#   filter(Unit == "Thousand Cubic Metres per day",
#          Variable == "In Situ Bitumen") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian In Situ Bitumen Production",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "k m³/day")
```

```{r}
#| include: false
Oil_In_Situ_Bitumen <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "In Situ Bitumen") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_In_Situ_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_In_Situ_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_In_Situ_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_In_Situ_Bitumen %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_In_Situ_Bitumen %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_In_Situ_Bitumen %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Mined Bitumen {.tabset-leaf}

```{r}
# EF2023$crude_oil_production %>%
#   filter(Unit == "Thousand Cubic Metres per day",
#          Variable == "Mined Bitumen") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Mined Bitumen Production",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "k m³/day")
```

```{r}
#| include: false
Oil_Mined_Bitumen <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Mined Bitumen") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_Mined_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_Mined_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_Mined_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_Mined_Bitumen %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_Mined_Bitumen %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_Mined_Bitumen %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Upgraded Bitumen {.tabset-leaf}

```{r}
#| include: false
Oil_Upgraded_Bitumen <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "(Upgraded Bitumen)") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_Upgraded_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_Upgraded_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_Upgraded_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_Upgraded_Bitumen %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_Upgraded_Bitumen %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_Upgraded_Bitumen %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Conventional Light {.tabset-leaf}

```{r}
# EF2023$crude_oil_production %>%
#   filter(Unit == "Thousand Cubic Metres per day",
#          Variable == "Conventional Light") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Conventional Light Production",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "k m³/day")
```

```{r}
#| include: false
Oil_Conventional_Light <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Conventional Light") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_Conventional_Light %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_Conventional_Light %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_Conventional_Light %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_Conventional_Light %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_Conventional_Light %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_Conventional_Light %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Field Condensate {.tabset-leaf}

```{r}
# EF2023$crude_oil_production %>%
#   filter(Unit == "Thousand Cubic Metres per day",
#          Variable == "Field Condensate") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Field Condensate Production",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "k m³/day")
```

```{r}
#| include: false
Oil_Field_Condensate <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Field Condensate") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_Field_Condensate %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_Field_Condensate %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_Field_Condensate %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_Field_Condensate %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_Field_Condensate %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_Field_Condensate %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Conventional Heavy {.tabset-leaf}

```{r}
# EF2023$crude_oil_production %>%
#   filter(Unit == "Thousand Cubic Metres per day",
#          Variable == "Conventional Heavy") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Conventional Heavy Production",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "k m³/day")
```

```{r}
#| include: false
Oil_Conventional_Heavy <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Conventional Heavy") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_Conventional_Heavy %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_Conventional_Heavy %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_Conventional_Heavy %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_Conventional_Heavy %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_Conventional_Heavy %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_Conventional_Heavy %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### C5+ {.tabset-leaf}

```{r}
# EF2023$crude_oil_production %>%
#   filter(Unit == "Thousand Cubic Metres per day",
#          Variable == "C5+") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian C5+ Production",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "k m³/day")
```

```{r}
#| include: false
Oil_C5_plus <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "C5+") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Oil_C5_plus %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Oil_C5_plus %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Oil_C5_plus %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Oil_C5_plus %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Oil_C5_plus %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Oil_C5_plus %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

### Hydrogen {.tabset}

#### Total* {.tabset-leaf}

```{r}
#| include: false
Hydrogen_Total_Calculated <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes") %>%
  summarize(Variable = "Total",
            Value = sum(Value),
            .by = c(Scenario, Region, Year)) %>% 
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Hydrogen_Total_Calculated %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Hydrogen_Total_Calculated %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Hydrogen_Total_Calculated %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Hydrogen_Total_Calculated %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Hydrogen_Total_Calculated %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Hydrogen_Total_Calculated %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Electrolysis {.tabset-leaf}

```{r}
# EF2023$hydrogen_production %>%
#   filter(Variable == "Electrolysis") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Hydrogen Production (Electrolysis)",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "Mt")
```

```{r}
#| include: false
Hydrogen_Electrolysis <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes",
         Variable == "Electrolysis") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Hydrogen_Electrolysis %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Hydrogen_Electrolysis %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Hydrogen_Electrolysis %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Hydrogen_Electrolysis %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Hydrogen_Electrolysis %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Hydrogen_Electrolysis %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Natural gas with CCS {.tabset-leaf}

```{r}
# EF2023$hydrogen_production %>%
#   filter(Variable == "Natural gas with CCS") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Hydrogen Production (Natural gas with CCS)",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "Mt")
```

```{r}
#| include: false
Hydrogen_Natural_Gas_With_CCS <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes",
         Variable == "Natural gas with CCS") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Hydrogen_Natural_Gas_With_CCS %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Hydrogen_Natural_Gas_With_CCS %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Hydrogen_Natural_Gas_With_CCS %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Hydrogen_Natural_Gas_With_CCS %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Hydrogen_Natural_Gas_With_CCS %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Hydrogen_Natural_Gas_With_CCS %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Biomass {.tabset-leaf}

```{r}
# EF2023$hydrogen_production %>%
#   filter(Variable == "Biomass") %>%
#   mutate(Region = Region %>% factor %>% fct_recode(
#     "AB" = "Alberta", "BC" = "British Columbia", "MN" = "Manitoba",
#     "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
#     "NS" = "Nova Scotia", "NT" = "Northwest Territories",
#     "NV" = "Nunavut", "ON" = "Ontario", "PEI" = "Prince Edward Island",
#     "QC" = "Quebec", "SK" = "Saskatchewan", "YK" = "Yukon",
#     "Canada" = "Canada") %>% fct_relevel("Canada", after = 0)) %>%
#   ridge_facet_plot(rp_X = Year,
#                    rp_Y = Value,
#                    rp_F1 = Scenario,
#                    rp_F2 = Region,
#                    rp_alpha = list(ribbons = 0.35),
#                    rp_title_main = "Canadian Hydrogen Production (Biomass)",
#                    rp_title_Y = "Production",
#                    rp_unit_abbrev = "Mt")
```

```{r}
#| include: false
Hydrogen_Biomass <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes",
         Variable == "Biomass") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Hydrogen_Biomass %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Hydrogen_Biomass %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Hydrogen_Biomass %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>%
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Hydrogen_Biomass %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Hydrogen_Biomass %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Hydrogen_Biomass %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

### Natural Gas {.tabset}

#### Total {.tabset-leaf}

```{r}
#| include: false
Natural_Gas_Total <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Total",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Natural_Gas_Total %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>%
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Natural_Gas_Total %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Natural_Gas_Total %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Natural_Gas_Total %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Natural_Gas_Total %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Natural_Gas_Total %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Tight {.tabset-leaf}

```{r}
#| include: false
Natural_Gas_Tight <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Tight",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Natural_Gas_Tight %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Natural_Gas_Tight %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Natural_Gas_Tight %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Natural_Gas_Tight %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Natural_Gas_Tight %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Natural_Gas_Tight %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Solution {.tabset-leaf}

```{r}
#| include: false
Natural_Gas_Solution <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Solution",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Natural_Gas_Solution %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Natural_Gas_Solution %>%
  filter(Year > 2022,
         # Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Natural_Gas_Solution %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Natural_Gas_Solution %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Natural_Gas_Solution %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Natural_Gas_Solution %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Non Associated {.tabset-leaf}

```{r}
#| include: false
Natural_Gas_Non_Associated <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Non Associated",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Natural_Gas_Non_Associated %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Natural_Gas_Non_Associated %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Natural_Gas_Non_Associated %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Natural_Gas_Non_Associated %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Natural_Gas_Non_Associated %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Natural_Gas_Non_Associated %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Shale {.tabset-leaf}

```{r}
#| include: false
Natural_Gas_Shale <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Shale",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Natural_Gas_Shale %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Natural_Gas_Shale %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Natural_Gas_Shale %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Natural_Gas_Shale %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Natural_Gas_Shale %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Natural_Gas_Shale %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Coalbed Methane {.tabset-leaf}

```{r}
#| include: false
Natural_Gas_Coalbed_Methane <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Coalbed Methane",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.dashboard-area-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Natural_Gas_Coalbed_Methane %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Natural_Gas_Coalbed_Methane %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e4343", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (", round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Natural_Gas_Coalbed_Methane %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#416070", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (", round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Natural_Gas_Coalbed_Methane %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Natural_Gas_Coalbed_Methane %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e4343", "#416070")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Natural_Gas_Coalbed_Methane %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = F),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::


# Financials

```{r}
#| include: false
Financials <- list()
#example: Financials$...$...
```

## _ {.tabset}

### Benchmark Prices {.tabset-leaf}

```{r}
#| include: false
Financials$Benchmark_Prices <- EF2023$benchmark_prices %>%
  mutate(Unit = Variable %>% str_extract("US\\$.*$"),
         Variable = Variable %>% str_remove_all(" - 2.*$") %>% str_remove_all(" \\(.*$")) %>% 
  mutate(Variable = Variable %>% factor %>% fct_recode(
    "WCS" = "Western Canadian Select", "WTI" = "West Texas Intermediate",
    "CLS" = "Canadian Light Sweet", "NIT" = "Nova Inventory Transfer"),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.financials-tab-column-grid}

```{r}
Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl") %>%
  mutate(Variable = Variable %>% fct_drop()) %>% 
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Variable, rp_F2 = Scenario,
                   rp_draw = list(ribbons = F, lines = F, smooth = T, medians = T, peaks = F),
                   rp_alpha = list(se = 0.25, points = 0.25),
                   rp_title_main = "Benchmarks in 2022 US$/bbl",
                   rp_title_Y = NA)
```

:::: {.financials-tab-column-2}

```{r}
Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu") %>%
  mutate(Variable = Variable %>% fct_drop()) %>% 
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Variable, rp_F2 = Scenario,
                   rp_draw = list(ribbons = F, lines = F, smooth = T, medians = T, peaks = F),
                   rp_alpha = list(se = 0.25, points = 0.25),
                   rp_title_main = "Benchmarks in 2022 US$/MMBtu",
                   rp_title_Y = NA)
```

::::: {.definition-area}

:::::: {.definition-area-title}

What do these represent?

::::::

:::::: {.definition-area-text}

**Brent**

A key global crude oil benchmark price. It is a light sweet grade extracted from the North Sea.

**Canadian Light Sweet (CLS)**

A light, sweet blend of conventionally produced crude oils in western Canada with an API gravity of around 40 degrees. It is typically priced at Edmonton, Alberta and is often called Edmonton Par Crude.

**West Texas Intermediate (WTI)**

A key North American benchmark crude oil price, it's a light sweet grade of crude oil produced in western Texas with an API gravity of 40 degrees.

**Western Canadian Select (WCS)**

A blend of Canadian heavy and bitumen sour crude oils mixed with sweet synthetic and condensates with an API gravity of about 21 degrees. It is priced at Hardisty, Alberta and is often used as a representative price for Canadian heavy crude oils.

**Henry Hub**

Henry Hub is the pricing point for natural gas futures traded on the New York Mercantile Exchange. The hub is located in Louisiana at the interconnection of numerous natural gas pipelines.

**Nova Inventory Transfer (NIT)**

The Nova Inventory Transfer, or NIT, is the pricing point used for natural gas sourced from the Western Canadian Sedimentary Basin (WCSB). As the natural gas trading hub located in Alberta, NIT is the commercial mechanism that overlays the Nova Gas Transmission Ltd. (NGTL) pipeline network, and is connected to several export markets and storage.

Source: EF2023.

::::::

:::::

::::

:::

### End Use Prices {.tabset-leaf}

```{r}
#| include: false
Financials$End_Use_Prices <- EF2023$end_use_prices
```

### Macro Indicators {.tabset-leaf}

```{r}
#| include: false
Financials$Macro_Indicators <- EF2023$macro_indicators
```
