---
title: "Dashboard"
format:
  dashboard:
    expandable: false
---

```{r}
#| message: false
#| warning: false
#| include: false

# install.packages("D:/MDi/Documents/R/package20260206", repos = NULL, type = "source")
# install.packages("tidyverse")
# install.packages("forcats")
# install.packages("bslib")
# install.packages("bsicons")

library(package20260206)
library(tidyverse)
library(plotly)
library(forcats)
library(bslib)
library(bsicons)
library(htmltools)
```

# Overview

```         
(See next tabs)

Dashboard Page
  ├ Overview
  ├ Production
  │ ├ Crude Oil
  │ │ ├ Total
  │ │ ├ (Upgraded Bitumen)
  │ │ ├ C5+
  │ │ ├ Conventional Heavy
  │ │ ├ Conventional Light
  │ │ ├ Field Condensate
  │ │ ├ In Situ Bitumen
  │ │ └ Mined Bitumen
  │ ├ Hydrogen
  │ │ ├ Total (calculated)
  │ │ ├ Biomass
  │ │ ├ Electrolysis
  │ │ └ Natural gas with CCS
  │ └ Natural Gas
  │   ├ Total
  │   ├ Solution
  │   ├ Non Associated
  │   ├ Tight
  │   ├ Shale
  │   └ Coalbed Methane
  ├ Financials
  │ ├ Benchmark Prices
  │ │ ├ Crude Oil
  │ │ └ Natural Gas
  │ ├ End Use Prices
  │ │ ├ ...
  │ │ ├ ...
  │ │ ├ ...
  │ │ └ ...
  │ └ Macro Indicators
  │   └ ...
  └ ...
```

# Production

```{r}
#| include: false
Production <- list()
#example: Production$Crude_Oil$Total
```

## _ {.tabset}

### Crude Oil {.tabset}

#### Total {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$Total <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Total") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$Total %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$Total %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$Total %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$Total %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$Total %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$Total %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### In Situ Bitumen {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$In_Situ_Bitumen <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "In Situ Bitumen") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$In_Situ_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$In_Situ_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$In_Situ_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$In_Situ_Bitumen %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$In_Situ_Bitumen %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$In_Situ_Bitumen %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Mined Bitumen {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$Mined_Bitumen <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Mined Bitumen") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$Mined_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$Mined_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$Mined_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$Mined_Bitumen %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$Mined_Bitumen %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$Mined_Bitumen %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Upgraded Bitumen {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$Upgraded_Bitumen <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "(Upgraded Bitumen)") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$Upgraded_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$Upgraded_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$Upgraded_Bitumen %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$Upgraded_Bitumen %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$Upgraded_Bitumen %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$Upgraded_Bitumen %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Conventional Light {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$Conventional_Light <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Conventional Light") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$Conventional_Light %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$Conventional_Light %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$Conventional_Light %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$Conventional_Light %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$Conventional_Light %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$Conventional_Light %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Field Condensate {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$Field_Condensate <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Field Condensate") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$Field_Condensate %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$Field_Condensate %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$Field_Condensate %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$Field_Condensate %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$Field_Condensate %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$Field_Condensate %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Conventional Heavy {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$Conventional_Heavy <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "Conventional Heavy") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$Conventional_Heavy %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$Conventional_Heavy %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$Conventional_Heavy %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$Conventional_Heavy %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$Conventional_Heavy %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$Conventional_Heavy %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### C5+ {.tabset-leaf}

```{r}
#| include: false
Production$Crude_Oil$C5_plus <- EF2023$crude_oil_production %>%
  filter(Unit == "Thousand Cubic Metres per day",
         Variable == "C5+") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Crude_Oil$C5_plus %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Crude_Oil$C5_plus %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Crude_Oil$C5_plus %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000) * 365.24}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Crude_Oil$C5_plus %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "k m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Crude_Oil$C5_plus %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Crude_Oil$C5_plus %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Crude Oil Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "k m³/day",
                   rp_labs_Y = list(digits = 0, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

### Hydrogen {.tabset}

#### Total (calculated) {.tabset-leaf}

```{r}
#| include: false
Production$Hydrogen$Total_Calculated <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes") %>%
  summarize(Variable = "Total",
            Value = sum(Value),
            .by = c(Scenario, Region, Year)) %>% 
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0),
    # Columns are added/ordered to reflect table structures in EF2023
    Unit = "Megatonnes", X = as.integer(NA)) %>% 
  select(X, Scenario, Unit, Region, Variable, Year, Value)
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Hydrogen$Total_Calculated %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Hydrogen$Total_Calculated %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Hydrogen$Total_Calculated %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Hydrogen$Total_Calculated %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Hydrogen$Total_Calculated %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Hydrogen$Total_Calculated %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2010, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Electrolysis {.tabset-leaf}

```{r}
#| include: false
Production$Hydrogen$Electrolysis <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes",
         Variable == "Electrolysis") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Hydrogen$Electrolysis %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Hydrogen$Electrolysis %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Hydrogen$Electrolysis %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Hydrogen$Electrolysis %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Hydrogen$Electrolysis %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Hydrogen$Electrolysis %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2010, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Natural gas with CCS {.tabset-leaf}

```{r}
#| include: false
Production$Hydrogen$Natural_Gas_With_CCS <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes",
         Variable == "Natural gas with CCS") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Hydrogen$Natural_Gas_With_CCS %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Hydrogen$Natural_Gas_With_CCS %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Hydrogen$Natural_Gas_With_CCS %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Hydrogen$Natural_Gas_With_CCS %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Hydrogen$Natural_Gas_With_CCS %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Hydrogen$Natural_Gas_With_CCS %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2010, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Biomass {.tabset-leaf}

```{r}
#| include: false
Production$Hydrogen$Biomass <- EF2023$hydrogen_production %>%
  filter(Unit == "Megatonnes",
         Variable == "Biomass") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Hydrogen$Biomass %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Hydrogen$Biomass %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_M = T)) %>% 
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Hydrogen$Biomass %>%
  filter(Year > 2022,
         Region == "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 1000000)}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_M = T)) %>%
  rp_format_proper() %>% 
  paste0(" t")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Hydrogen$Biomass %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "Mt"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Hydrogen$Biomass %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Hydrogen$Biomass %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Hydrogen Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "Mt",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2010, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

### Natural Gas {.tabset}

#### Total {.tabset-leaf}

```{r}
#| include: false
Production$Natural_Gas$Total <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Total",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Natural_Gas$Total %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>%
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Natural_Gas$Total %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Natural_Gas$Total %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Natural_Gas$Total %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Natural_Gas$Total %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Natural_Gas$Total %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Tight {.tabset-leaf}

```{r}
#| include: false
Production$Natural_Gas$Tight <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Tight",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Natural_Gas$Tight %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Natural_Gas$Tight %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Natural_Gas$Tight %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Natural_Gas$Tight %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Natural_Gas$Tight %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Natural_Gas$Tight %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Solution {.tabset-leaf}

```{r}
#| include: false
Production$Natural_Gas$Solution <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Solution",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Natural_Gas$Solution %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Natural_Gas$Solution %>%
  filter(Year > 2022,
         # Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Natural_Gas$Solution %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Natural_Gas$Solution %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Natural_Gas$Solution %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Natural_Gas$Solution %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Non Associated {.tabset-leaf}

```{r}
#| include: false
Production$Natural_Gas$Non_Associated <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Non Associated",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Natural_Gas$Non_Associated %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Natural_Gas$Non_Associated %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Natural_Gas$Non_Associated %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Natural_Gas$Non_Associated %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Natural_Gas$Non_Associated %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Natural_Gas$Non_Associated %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Shale {.tabset-leaf}

```{r}
#| include: false
Production$Natural_Gas$Shale <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Shale",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Natural_Gas$Shale %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Natural_Gas$Shale %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Natural_Gas$Shale %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Natural_Gas$Shale %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Natural_Gas$Shale %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Natural_Gas$Shale %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

#### Coalbed Methane {.tabset-leaf}

```{r}
#| include: false
Production$Natural_Gas$Coalbed_Methane <- EF2023$natural_gas_production %>%
  filter(Unit == "Million Cubic Metres per day",
         Variable == "Coalbed Methane",
         Region != "Western Canadian Sedimentary Basin") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

::: {.production-tab-column-grid}

:::: {.card-row-grid}

```{r}
### Card: Current Measures total (1/3)
v1 <- Production$Natural_Gas$Coalbed_Methane %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Current Measures") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v1 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#777", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", "Current measures (baseline)"))
###
```

```{r}
### Card: Canada Net-zero total (2/3)
v2 <- Production$Natural_Gas$Coalbed_Methane %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Canada Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v2 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Global Net-zero total (3/3)
v3 <- Production$Natural_Gas$Coalbed_Methane %>%
  filter(Year > 2022,
         Region != "Canada",
         Scenario == "Global Net-zero") %>%
  pull(Value) %>%
  {sum(. * 365.24) * 1000000}

value_box_value <- v3 %>%
  # rp_format_proper2(format = list(do_B = T)) %>% 
  rp_format_proper() %>% 
  paste0(" m³")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Total (2023–2050)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Top contributor (Region)
# Get top contributor (Region)
value_box_data <- Production$Natural_Gas$Coalbed_Methane %>%
  filter(Region != "Canada") %>%
  # Compute averages and contributions
  summarize(Value_Total = mean(Value),
            Value_Average = mean(Value),
            .by = Region) %>%
  mutate(Value_Percentage = Value_Total / sum(Value_Total)) %>% 
  # Get highest contribution
  arrange(desc(Value_Percentage)) %>%
  head(1) %>% 
  # Prepare labels
  mutate(Line_1 = paste0("Averaging ", round(Value_Average, 1), "M m³/day"),
         Line_2 = paste0("Contributing ", round(100 * Value_Percentage, 0), "% (avg.)"))
value_box_value <- value_box_data$Region
value_box_tag_1 <- value_box_data$Line_1
value_box_tag_2 <- value_box_data$Line_2

# Prepare showcase plot
value_box_plot <- Production$Natural_Gas$Coalbed_Methane %>% 
  filter(Region == value_box_data$Region) %>%
  ggplot(aes(x = Year, y = Value, group = Scenario,
             col = Scenario, fill = Scenario,
             ymin = pmin(0, Value), ymax = pmax(0, Value))) +
  geom_ribbon(col = NULL, fill = "#AAA", alpha = 0.1) +
  geom_line(aes(text = paste0(round(Value, 1), ": ", Scenario, " (", Year, ")")),
            alpha = 0.25, lwd = 0.25) +
  scale_color_discrete(palette = c("#777", "#7e3434", "#256175")) +
  theme_void() +
  theme(legend.position = "none")
value_box_plot <- ggplotly(value_box_plot, tooltip = "text") %>%
  layout(plot_bgcolor = "rgba(1,1,1,0)", hovermode = "x",
         hoverlabel = list(font = list(family = "Onest", size = 13)),
         xaxis = list(fixedrange = TRUE), yaxis = list(fixedrange = TRUE)) %>%
  config(displayModeBar = F)

# Draw value box
value_box(theme = value_box_theme(bg = "#EEE", fg = "#777"),
        title = "Top contributor",
        showcase = value_box_plot,
        showcase_layout = "bottom",
        value = value_box_value,
        # tag("p", value_box_tag_1),
        tag("p", value_box_tag_2))
###

```

::::

:::: {.plotly-grid}

```{r}
# Main plot
Production$Natural_Gas$Coalbed_Methane %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Region,
                   rp_title_main = "Canadian Natural Gas Production",
                   rp_title_Y = "Production", rp_unit_abbrev = "M m³/day",
                   rp_labs_Y = list(digits = 1, do_k = F, do_e = F),
                   rp_draw = list(points = F, peaks = T, medians = F,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2005, 2022, 2030, 2035, 2050))),
                   rp_alpha = list(ribbons = 0.35))
```

::::

:::

# Financials

```{r}
#| include: false
Financials <- list()
#example: Financials$...$...
```

## _ {.tabset}

### Benchmark Prices {.tabset}

```{r}
#| include: false
Financials$Benchmark_Prices <- EF2023$benchmark_prices %>%
  mutate(Unit = Variable %>% str_extract("US\\$.*$"),
         Variable = Variable %>% str_remove_all(" - 2.*$") %>% str_remove_all(" \\(.*$")) %>% 
  mutate(Variable = Variable %>% factor %>% fct_recode(
    "WCS" = "Western Canadian Select", "WTI" = "West Texas Intermediate",
    "CLS" = "Canadian Light Sweet", "NIT" = "Nova Inventory Transfer"),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

#### Crude Oil {.tabset-leaf}

::: {.financials-tab-column-grid}

:::: {.plotly-grid}

```{r}
Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl") %>%
  mutate(Variable = Variable %>% fct_drop()) %>%
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Variable,
                   rp_draw = list(ribbons = F, lines = F, smooth = T, medians = F, peaks = T,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2022))),
                   
                   rp_alpha = list(se = 0.25, points = 0.25),
                   rp_title_main = "Crude Oil Benchmarks",
                   rp_title_Y = "Prices ($/bbl*)")
```

::::

:::: {.financials-tab-column-2}

::::: {.definition-area}

:::::: {.definition-area-title}

What do these represent?

::::::

:::::: {.definition-area-text}

**Brent**

A key global crude oil benchmark price. It is a light sweet^[Low-sulfur, easier to refine] grade extracted from the North Sea^[API gravity for the Brent benchmark is cited to be just above 38 degrees.].

**Canadian Light Sweet (CLS)**

A light, sweet blend of conventionally produced crude oils in western Canada with an API gravity of around 40 degrees^[A density equivalent of around 824 kg/m³ (at 15°C)]. It is typically priced at Edmonton, Alberta and is often called Edmonton Par Crude.

**West Texas Intermediate (WTI)**

A key North American benchmark crude oil price, it's a light sweet grade of crude oil produced in western Texas with an API gravity of 40 degrees.

**Western Canadian Select (WCS)**

A blend of Canadian heavy and bitumen sour^[High-sulfur, harder to refine] crude oils mixed with sweet synthetic and condensates with an API gravity of about 21 degrees. It is priced at Hardisty, Alberta and is often used as a representative price for Canadian heavy crude oils.

Source: EF2023^[For more definitions, refer to [CER's Energy Information Program - Glossary](https://www.cer-rec.gc.ca/en/data-analysis/glossary)], with added footnotes.

------------------------------------------------------------------------

**WTI-WCS price differential**

A measure of crude oil market favorability. The interpretation for Canada is that heavy crude oil can be sold more easily if the differential is narrow^[e.g., Below 15 US$/bbl], indicating a demand strong enough to offset heavy refining costs.

------------------------------------------------------------------------

**Sensitivity metric**

A custom metric normalizing the average amount by which new scenarios offset the baseline. For instance, a sensitivity metric of 0.19 would be found if, for each individual year, the net-zero scenarios shifted the normal price up or down by about 20%^[The reference point is updated year by year. The metric is also averaged across new scenarios.
**Example:** If one scenario halves the baseline and another keeps it unchanged, the metric is 0.25.
This is because half of the baseline was subtracted by one of the two scenarios, adding 0.25 to the pooled metric.].

------------------------------------------------------------------------

\***Note:** Prices per oil barrel^[1 bbl is ~0.159 m³] are in **2022** US dollars.

::::::

:::::

::::: {.financials-tab-card-grid}

:::::: {.card-row-grid}

```{r}
### Card: Average projected differential (2023-2025), WTI-WCS, Current Measures (1/3)
v1 <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl",
         Year > 2022,
         Variable %in% c("WCS", "WTI"),
         Scenario == "Current Measures") %>%
  mutate(across(where(is.factor), ~ fct_drop(.))) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute the average differential
  reduce(`-`) %>% { -. } %>% mean()

value_box_value <- v1 %>%
  rp_format_proper() %>% 
  paste0(" $/bbl*")

value_box(theme = value_box_theme(bg = "#777", fg = "#eee"),
        title = "Average WTI-WCS differential (2023-2025)",
        value = value_box_value,
        tag("p", "Current Measures (baseline)"))
###
```

```{r}
### Card: Average projected differential (2023-2025), WTI-WCS, Canada Net-zero (2/3)
v2 <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl",
         Year > 2022,
         Variable %in% c("WCS", "WTI"),
         Scenario == "Canada Net-zero") %>%
  mutate(across(where(is.factor), ~ fct_drop(.))) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute the average differential
  reduce(`-`) %>% { -. } %>% mean()

value_box_value <- v2 %>%
  rp_format_proper() %>%
  paste0(" $/bbl*")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Average WTI-WCS differential (2023-2025)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Average projected differential (2023-2025), WTI-WCS, Global Net-zero (3/3)
v3 <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl",
         Year > 2022,
         Variable %in% c("WCS", "WTI"),
         Scenario == "Global Net-zero") %>%
  mutate(across(where(is.factor), ~ fct_drop(.))) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute the average differential
  reduce(`-`) %>% { -. } %>% mean()

value_box_value <- v3 %>%
  rp_format_proper() %>%
  paste0(" $/bbl*")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Average WTI-WCS differential (2023-2025)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

::::::

:::::: {.card-row-grid}

```{r}
### Card: Most sensitive benchmark (1/2)
value_box_value <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl") %>%
  mutate(Variable = Variable %>% fct_drop()) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) {split(x, x$Scenario)}) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute sensitivity by benchmark (average accumulated change in scale from baseline)
  sapply(\(x) {mean( sqrt( colSums((x[, -1]/x[, 1] - 1)^2) / nrow(x) ) )}) %>%
  # Get most/least sensitive benchmark
  sort(decreasing = T) %>% head(1)

value_box(theme = value_box_theme(bg = "#eee", fg = "#aaa"),
        title = "Most sensitive benchmark",
        value = value_box_value %>% names(),
        tag("p", paste0("(Sensitivity metric: ",
                        value_box_value %>% rp_format_proper(format = list(digits = 2)),
                        ")")))
###
```

```{r}
### Card: Most stable benchmark (2/2)
value_box_value <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/bbl") %>%
  mutate(Variable = Variable %>% fct_drop()) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute sensitivity by benchmark (average accumulated change in scale from baseline)
  sapply(\(x) {mean( sqrt( colSums((x[, -1]/x[, 1] - 1)^2) / nrow(x) ) )}) %>%
  # Get most/least sensitive benchmark
  sort() %>% head(1)

value_box(theme = value_box_theme(bg = "#eee", fg = "#aaa"),
        title = "Most stable benchmark",
        value = value_box_value %>% names(),
        tag("p", paste0("(Sensitivity metric: ",
                        value_box_value %>% rp_format_proper(format = list(digits = 2)),
                        ")")))
###
```

::::::

:::::

::::

:::

#### Natural Gas {.tabset-leaf}

::: {.financials-tab-column-grid}

:::: {.plotly-grid}

```{r}
Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu") %>%
  mutate(Variable = Variable %>% fct_drop()) %>% 
  ridge_facet_plot(rp_X = Year, rp_Y = Value, rp_F1 = Scenario, rp_F2 = Variable,
                   rp_draw = list(ribbons = F, lines = F, smooth = T, medians = F, peaks = T,
                                  peaks_at = list(Y_min = F, Y_max = F,
                                                  X_values = c(2022))),
                   rp_alpha = list(se = 0.25, points = 0.25),
                   rp_title_main = "Natural Gas Benchmarks",
                   rp_title_Y = "Prices ($/MMBtu*)")
```

::::

:::: {.financials-tab-column-2}

::::: {.definition-area}

:::::: {.definition-area-title}

What do these represent?

::::::

:::::: {.definition-area-text}

**Henry Hub**

Henry Hub is the pricing point for natural gas futures traded on the New York Mercantile Exchange. The hub is located in Louisiana at the interconnection of numerous natural gas pipelines.

**Nova Inventory Transfer (NIT)**

The Nova Inventory Transfer, or NIT, is the pricing point used for natural gas sourced from the Western Canadian Sedimentary Basin (WCSB). As the natural gas trading hub located in Alberta, NIT is the commercial mechanism that overlays the Nova Gas Transmission Ltd. (NGTL) pipeline network, and is connected to several export markets and storage.

Source: EF2023^[For more definitions, refer to [CER's Energy Information Program - Glossary](https://www.cer-rec.gc.ca/en/data-analysis/glossary)], with added footnotes.

------------------------------------------------------------------------

**Henry Hub-NIT price differential**

A measure of natural gas market favorability. The interpretation for Canada is that heavy crude oil can be sold more easily if the differential is narrow^[e.g., Below 15 US$/bbl], indicating a demand strong enough to offset heavy refining costs.

------------------------------------------------------------------------

**Sensitivity metric**

A custom metric normalizing the average amount by which new scenarios offset the baseline. For instance, a sensitivity metric of 0.27 would be found if, for each individual year, the net-zero scenarios shifted the normal price up or down by 27%^[The reference point is updated year by year. The metric is also averaged across new scenarios.
**Example:** If one scenario halves the baseline and another keeps it unchanged, the metric is 0.25.
This is because half of the baseline was subtracted by one of the two scenarios, adding 0.25 to the pooled metric.].

------------------------------------------------------------------------

\***Note:** Prices per million British thermal unit^[1 MMBtu is ~1.055 Gigajoules] are in **2022** US dollars.

::::::

:::::

::::: {.financials-tab-card-grid}

:::::: {.card-row-grid}

```{r}
### Card: Average projected differential (2023-2025), Henry Hub-NIT, Current Measures (1/3)
v1 <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu",
         Year > 2022,
         Variable %in% c("Henry Hub", "NIT"),
         Scenario == "Current Measures") %>%
  mutate(across(where(is.factor), ~ fct_drop(.))) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute the average differential
  reduce(`-`) %>% mean()

value_box_value <- v1 %>%
  rp_format_proper() %>% 
  paste0(" $/MMBtu*")

value_box(theme = value_box_theme(bg = "#777", fg = "#eee"),
        title = "Average Henry Hub-NIT differential (2023-2025)",
        value = value_box_value,
        tag("p", "Current Measures (baseline)"))
###
```

```{r}
### Card: Average projected differential (2023-2025), Henry Hub-NIT, Canada Net-zero (2/3)
v2 <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu",
         Year > 2022,
         Variable %in% c("Henry Hub", "NIT"),
         Scenario == "Canada Net-zero") %>%
  mutate(across(where(is.factor), ~ fct_drop(.))) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute the average differential
  reduce(`-`) %>% mean()

value_box_value <- v2 %>%
  rp_format_proper() %>%
  paste0(" $/MMBtu*")

value_box(theme = value_box_theme(bg = "#7e3434", fg = "#EEE"),
        title = "Average Henry Hub-NIT differential (2023-2025)",
        value = value_box_value,
        tag("p", paste0("Canada Net-zero", " (",
                        switch(as.character(sign(v2-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v2/v1 - 1) * 100), "%)")))
###
```

```{r}
### Card: Average projected differential (2023-2025), Henry Hub-NIT, Global Net-zero (3/3)
v3 <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu",
         Year > 2022,
         Variable %in% c("Henry Hub", "NIT"),
         Scenario == "Global Net-zero") %>%
  mutate(across(where(is.factor), ~ fct_drop(.))) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute the average differential
  reduce(`-`) %>% mean()

value_box_value <- v3 %>%
  rp_format_proper() %>%
  paste0(" $/MMBtu*")

value_box(theme = value_box_theme(bg = "#256175", fg = "#EEE"),
        title = "Average Henry Hub-NIT differential (2023-2025)",
        value = value_box_value,
        tag("p", paste0("Global Net-zero", " (",
                        switch(as.character(sign(v3-v1)),
                               "1" = "▲", "0" = "►", "-1" = "▼"),
                        round((v3/v1 - 1) * 100), "%)")))
###
```

::::::

:::::: {.card-row-grid}

```{r}
### Card: Most sensitive benchmark (1/2)
value_box_value <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu") %>%
  mutate(Variable = Variable %>% fct_drop()) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) {split(x, x$Scenario)}) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute sensitivity by benchmark (average accumulated change in scale from baseline)
  sapply(\(x) {mean( sqrt( colSums((x[, -1]/x[, 1] - 1)^2) / nrow(x) ) )}) %>%
  # Get most/least sensitive benchmark
  sort(decreasing = T) %>% head(1)

value_box(theme = value_box_theme(bg = "#eee", fg = "#aaa"),
        title = "Most sensitive benchmark",
        value = value_box_value %>% names(),
        tag("p", paste0("(Sensitivity metric: ",
                        value_box_value %>% rp_format_proper(format = list(digits = 2)),
                        ")")))
###
```

```{r}
### Card: Most stable benchmark (2/2)
value_box_value <- Financials$Benchmark_Prices %>%
  filter(Unit == "US$/MMBtu") %>%
  mutate(Variable = Variable %>% fct_drop()) %>%
  # Subset by benchmark
  split(paste(.$Variable)) %>%
  # Sub-subset by scenario
  lapply(\(x) { split(x, x$Scenario) }) %>%
  # Get prices for all years
  lapply(\(x) sapply(x, pull, "Value", "Year")) %>%
  # Compute sensitivity by benchmark (average accumulated change in scale from baseline)
  sapply(\(x) {mean( sqrt( colSums((x[, -1]/x[, 1] - 1)^2) / nrow(x) ) )}) %>%
  # Get most/least sensitive benchmark
  sort() %>% head(1)

value_box(theme = value_box_theme(bg = "#eee", fg = "#aaa"),
        title = "Most stable benchmark",
        value = value_box_value %>% names(),
        tag("p", paste0("(Sensitivity metric: ",
                        value_box_value %>% rp_format_proper(format = list(digits = 2)),
                        ")")))
###
```

::::::

:::::

::::

:::

### End Use Prices {.tabset}

#### Commercial {.tabset-leaf}

```{r}
#| include: false
Financials$End_Use_Prices$Commercial <- EF2023$end_use_prices %>%
  filter(Sector == "Commercial") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

```{r}
local({
    
    library(tidyverse)
    library(plotly)
    library(package20260206)
    library(scales)
    
    # Function to prepare a df (with factors and a value) for an icicle/sunburst chart
    as_sunburst_icicle_df <- function(df, factor_cols, value_col, frame_col,
                                      # hcl_palette = "Light Grays",
                                      color_root = "#157", color_leaf = "white",
                                      alpha_min = 0, alpha_max = 1) {
      
        # FRAMES
        RESULT <- data.frame()
        # FRAMES
        frames <- unique(df[[frame_col]])
        # FRAMES
        daf <- df
        # FRAMES
        for (frame in frames) {
          # FRAMES
          # print(frame)
          # FRAMES
          df <- daf %>% filter(!!sym(frame_col) == frame)
          # FRAMES
          # print(df %>% tibble)
          

        result <- data.frame()
        
        # 1. Initialize nodes for the plot and record their depth (i)
        for (i in seq_along(factor_cols)) {
            group_cols <- factor_cols[1:i]
            agg <- df %>%
                group_by(across(all_of(group_cols))) %>%
                summarise(total = sum(!!sym(value_col)),
                          average = mean(!!sym(value_col)),
                          .groups = "drop") %>%
                mutate(id = apply(.[, group_cols, drop=FALSE], 1, paste, collapse = "-"),
                       label = as.character(.[[tail(group_cols, 1)]]),
                       parent = if(i == 1) "Total" else apply(.[, factor_cols[1:(i-1)], drop=FALSE], 1, paste, collapse = "-"),
                       depth = i)
            result <- bind_rows(result, agg[, c("id", "label", "parent", "total", "depth", "average")])
        }
        
        # 2. Add the root (total) node (depth = 0)
        result <- bind_rows(result, data.frame(id = "Total", label = "", parent = "",
                                               total = sum(df[[value_col]]), average = mean(df[[value_col]]),
                                               depth = 0))
        
        # 3. Map color by depth and alpha by siblings
        # pal <- hcl.color(max(result$depth) + 1, hcl_palette)
        # rgb_mat <- col2rgb(pal[result$depth + 1])
        depth_colors <- colorRampPalette(c(color_root, color_leaf))(max(result$depth) + 1)
        rgb_mat <- col2rgb(depth_colors[result$depth + 1])
        result <- result %>%
            group_by(parent) %>%
            # Category-wise alphas
            # mutate(alpha = rescale(total, from = c(0, max(total)), to = c(alpha_min, alpha_max)) ) %>%
            # Global alphas
            mutate(alpha = rescale(total, from = c(0, max(result$total)), to = c(alpha_min, alpha_max)) ) %>%
            ungroup() %>%
            mutate(color = sprintf("rgba(%d,%d,%d,%f)", rgb_mat[1,], rgb_mat[2,], rgb_mat[3,], alpha))
        
        # !FRAMES
        # return(result)
        # FRAMES
        print(RESULT %>% tibble)
        # FRAMES
        RESULT <- RESULT %>% rbind(result %>% cbind(frame = frame))
        
        #FRAMES
        }
        #FRAMES
        return(RESULT)
    }
    
    
    # Data
    df <- EF2023$end_use_prices %>%
        mutate(Region = Region %>% factor %>% fct_recode(
            "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
            "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
            "NS" = "Nova Scotia", "NT" = "Northwest Territories",
            "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
            "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
            "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
            Scenario = Scenario %>% fct_relevel("Current Measures", after = 0)) %>%
        filter(Scenario == "Current Measures",
               Year > 2022) %>%
        summarize(Value = mean(Value), .by = c(Scenario, Region, Variable, Sector))
    
    # print(df %>% tibble)
    
    # Function call
    # df_plot <- as_sunburst_icicle_df(df, c("Scenario", "Region", "Variable", "Sector"), "Value")
    df_plot <- as_sunburst_icicle_df(df,
                                     # c("Scenario", "Region", "Variable", "Sector"), "Value",
                                     # c("Scenario", "Sector", "Variable", "Region"), "Value",
                                     # c("Scenario", "Variable", "Sector"), "Value",
                                     # c("Variable", "Sector", "Region"), "Value",
                                     # c("Sector", "Variable", "Region"), "Value",
                                     # c("Variable", "Sector"), "Value",
                                     # c("Sector", "Variable", "Region"), "Value", "Scenario",
                                     c("Sector", "Variable"), "Value", "Region",
                                     # color_root = "#EAA", color_leaf = "#511",
                                     # color_root = "#9EA", color_leaf = "#151",
                                     color_root = "#7CE", color_leaf = "#115",
                                     alpha_min = 0.1, alpha_max = 1)
    
    # print(df_plot %>% tibble)
    
    
    # Sunburst/icicle chart
    fig <- plot_ly(data = df_plot,
                   type = 'icicle',
                   ids = ~id,
                   labels = ~label,
                   parents = ~parent,
                   values = ~total,
                   frame = ~frame,
                   text = ~rp_format_proper(average),
                   marker = ~list(colors = color,
                                  line = list(width = 0)),
                   tiling = list(orientation = "v", pad = 17),
                   textposition = "middle center",
                   # textinfo = "label+text+percent parent",
                   textinfo = "label+text",
                   hoverinfo = "none",
                   # hoverlabel = list(font = list(size = 17, color = "black"), bordercolor = "#FFFFFF00"),
                   pathbar = list(side = "bottom"),
                   
                   # Ensures parent size = sum of children
                   branchvalues = 'total') %>%
        layout(title = "Current Measures",
               font = list(size = 21, family = "Onest Medium"),
               margin = list(l = 0, r = 0, t = 31, b = 31)) %>%
      animation_opts(frame = 5000, transition = 700, easing = "cubic-out", redraw = F) %>% 
      animation_button(visible = F) %>% 
      animation_slider(bordercolor = "#FFFFFF00", tickcolor = "#FFFFFF00", currentvalue = list(visible = F))

    fig
    
    # Source: Initial tier logic via Claude Haiku 4.5 (via Duck.ai), edited for color via Gemini, then hand-refined (refactored, frame-by-frame code added, style).
})

```


#### Industrial {.tabset-leaf}

```{r}
#| include: false
Financials$End_Use_Prices$Industrial <- EF2023$end_use_prices %>%
  filter(Sector == "Industrial") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

#### Residential {.tabset-leaf}

```{r}
#| include: false
Financials$End_Use_Prices$Residential <- EF2023$end_use_prices %>%
  filter(Sector == "Residential") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

#### Transportation {.tabset-leaf}

```{r}
#| include: false
Financials$End_Use_Prices$Transportation <- EF2023$end_use_prices %>%
  filter(Sector == "Transportation") %>%
  mutate(Region = Region %>% factor %>% fct_recode(
    "AB" = "Alberta", "BC" = "British Columbia", "MB" = "Manitoba",
    "NB" = "New Brunswick", "NL" = "Newfoundland and Labrador",
    "NS" = "Nova Scotia", "NT" = "Northwest Territories",
    "NU" = "Nunavut", "ON" = "Ontario", "PE" = "Prince Edward Island",
    "QC" = "Quebec", "SK" = "Saskatchewan", "YT" = "Yukon",
    "Canada" = "Canada") %>% fct_relevel("Canada", after = 0),
    Scenario = Scenario %>% fct_relevel("Current Measures", after = 0))
```

### Macro Indicators {.tabset-leaf}

```{r}
#| include: false
Financials$Macro_Indicators <- EF2023$macro_indicators

# Variable has:
# "Real Gross Domestic Product ($2012 Millions)"
# "Population (thousands)"
# "Gross Domestic Product Deflator (2012=100)"
# "Consumer Price Index (2002=100)"
# "Canada-US Exchange Rate (C$/US$)"

```





<!--
# Development notes:

## Changed since last commit:
- Financials > Natural Gas completed
- Financials > Benchmark Prices: Sensitivity metrics need to be explained

## Open (has impact):
- Idea: Landing page: 4 cards: Demand, Financials, Production, Emissions
- Idea: Main page per tab. Starts as:
Production %>% lapply(\(x) {
    x$To %>% tibble %>%
        select(-X)
})
- Financials: Narrow viewport CSS should be improved
- Production > Crude Oil: Units bbl would match Financials > Benchmark Prices better

## Open (has low/no impact):
- CSS: Screen width range 600px-576px places the scrollbar in the dashboard area (expected: the page).
- CSS: The total height could be capped (try zooming in/out in-browser)

-->
